---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
devtools::load_all()
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pkggraph

<!-- badges: start -->
<!-- badges: end -->

> Explore various dependencies of a package(s) (on the Comprehensive R Archive Network Like repositories).

## Utilities

Start with `init()` which gets metadata from a CRAN like repository.

The package offers four functions:

1. `get_dependencies()`: Get direct or indirect dependencies of a set of packages at desired depth (as a dataframe).
2. `get_neighborhood()`: Get both direct and indirect of a set of packages at desired depth (as a dataframe).
3. `as_graph()`: Get metadata embedded `igraph` equivalent of a dependency dataframe.
4. `plot()`: Static plot of dependency graph.

## Example

```{r}
suppressPackageStartupMessages(library("dplyr"))
init()

# what does `mboost` package do
packmeta |> filter(Package == "mboost") |> pull(Description) |> cat()

# Get direct 'import' dependencies of `mboost` two levels deeper
get_dependencies("mboost", level = 2, relation = "Imports")

# Get neighborhood (direct and indirect) dependencies (of all types) of `mboost` one level deeper
get_neighborhood("mboost", level = 1)

# convert a dependency dataframe to a graph
get_neighborhood("mboost", level = 1) |> as_graph()

# plot a dependency graph
get_neighborhood("mboost", level = 1, relation = "Imports") |> as_graph() |> plot()
```

## Installation

From CRAN:

``` r
pak::pkg_install("pkggraph")
```

You can install the development version of pkggraph from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("talegari/pkggraph")
```
